Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-09 paper/tv.tex
m

\begin{comment}
  we express, the effects of \code{send(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
\end{align*}  
effects of \code{addSugar(n)} as:
\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {\small
         \begin{enumerate}
\item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
      \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
    \item 
     ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addSugar(n\text{-}1)} }}
      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} }\}} 
     \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} ) }}
      \\
       \item 
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{send(n)}}}}\\

@@

\begin{prooftree}
\Hypo{
\code{\textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
}  \Rightarrow 
\textcolor {darkred}{t_R {<}3}
} \qquad
\code{emp  \CONTAIN  \_^\star}
}
\Infer[dashed]1[{\siderule{\textcircled{8}[PROVE]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  emp
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \_^\star}}
\Infer[dashed]1[{\siderule{\textcircled{7}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  \cancel{\{Go\}}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
\Infer[dashed]1[{\siderule{\textcircled{6}[Normalization]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee  \_^\star}}
\Infer[dashed]1[{\siderule{\textcircled{5}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} 
:  \cancel{\{ Ready\}} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
\Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
 } : \cancel{\{Cook\} \mysharp  t_L^2} \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\mysharp  t_R}\cdot\_^\star}  }
\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\mysharp  t_L^1} \cdot \{Cook\} \mysharp  t_L^2 \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\_}\cdot\{Cook\}\mysharp  t_R \cdot\_^\star}  }
\Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t_L \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \_\cdot\{Cook\}\mysharp  t_R\cdot\_^\star}  }
 \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t {<}3} : \_\cdot\{Cook\}\mysharp  t\cdot\_^\star}  }
\end{prooftree}}
\\~\\

>>>>

\begin{comment}
  we express, the effects of \code{addSugar(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
\end{align*}  
effects of \code{addSugar(n)} as:
\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {\small
         \begin{enumerate}
\item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
      \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
    \item 
     ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addSugar(n\text{-}1)} }}
      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} }\}} 
     \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} ) }}
      \\
       \item 
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addSugar(n)}}}}\\

@@

\begin{prooftree}
\Hypo{
  \code{\siderule{[Prove]}}
}

\Infer[dashed]1[]{ \code{ n{=}0 \wedge \epsilon 
\CONTAIN t_r{\geq}0 \wedge \epsilon \mysharp t_r}}

\Infer[dashed]1[]{ \code{ n{=}0 \wedge Sugar
\CONTAIN t_r{\geq}0 \wedge Sugar \mysharp t_r}}

\Hypo{
  \code{\textcolor {darkred}{  t{>}1 {\wedge} t_l{\geq}(n\text{-}1) 
   {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1  \Rightarrow t_r{\geq}n
}  } 
\code{\siderule{[Prove]}}
 }

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
 \epsilon
\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1 
\wedge \epsilon}}

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
 Sugar \mysharp t_l
\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t
\wedge Sugar \mysharp t_r^1}}

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l
\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r}}

\Infer[dashed]2[]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l) } 
\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r  }

\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } 
\CONTAIN \effect_{post}^{addSugar(n)}  }
\end{prooftree}}
\\~\\
